\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
Carnegie Mellon University\\
Master of Information Technology Strategy (MITS) Program}

% opening here
\opening{To the admissions committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

This letter of recommendation is for MIDN 1/C Jisub Lim, who has applied to the Master of Information Technology Strategy (MITS) Program at Carnegie Mellon. Mr Lim is a good candidate worthy of consideration for your program. Mr Lim is a good student with a 3.85 GPA who has studied abroad in Korea. Within my department, he has taken the emerging technologies elective, which led him to his interest in data analytics and artificial intelligence. He has maintained good academic performance while taking on a number of billets and leadership positions within the brigade. As a student in my section of ES200 (Introduction to Systems Engineering) I was impressed by his team’s design of a mechatronic dancing bear.

I was Mr Lim’s advisor for an ambitious capstone project to fly unmanned aerial systems to survey and return botanical samples from a remote island. As a future naval aviator, Mr Lim has learned much regarding project management, quadrotor flight operations from a RHIB, and engineering tradeoffs between battery life, stability, ability to hold position with and without auxiliary sensors, and payload. He had to balance project schedule, safety of flight, engineering challenges, and external events (such as parts availability and the global coronavirus situation) in ways above and beyond what normal capstone projects face. The project had aspects of machine vision, deep learning, autonomy, and the ethics (and regulaton) of drones and autonomy in a conservation/biodiversity situation. I believe he will learn even more if given the opportunity in the MITS program.



\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}