\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
}

% opening here
\opening{To the Admissions Committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

This letter of recommendation is for MIDN 1/C Jisub Lim, who has applied to pursue a master's degree in Operations Research at Naval Postgraduate School. Mr Lim is a good candidate worthy of consideration for your program. 

Mr Lim is a good student with a 3.85 GPA who has studied abroad in Korea. Within my department, he has taken the Engineering Economics elective concentration, leading to his interest in Operations Research. He has maintained good academic performance while taking on a number of billets and leadership positions within the brigade. As a student in my section of ES200 (Introduction to Systems Engineering) I was impressed by his team's design of a mechatronic dancing bear. 

I am Mr Lim's advisor for an ambitious capstone project to fly unmanned aerial systems to survey and return botanical samples from a remote island. As a future naval aviator, Mr Lim has learned much regarding project management, quadrotor flight operations from a RHIB, and engineering tradeoffs between battery life, stability, ability to hold position with and without auxiliary sensors, and payload. He is currently balancing project schedule, safety of flight, engineering challenges, and external events (such as parts availability and the global coronavirus situation) in ways above and beyond what normal capstone projects face. I believe he will learn even more if given the opportunity to pursue an Operations Research master's degree at NPS. 

\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}

%I am currently applying for the Aviation Stash Program to pursue a master's degree at NPS before I head to flight school and having had the privilege to take many of your classes during my time here, I was wondering if you would be willing to write a letter of recommendation for my application. This will be read to evaluate my potential and ability to complete a master's program based on my academic performance during my four years here. There isn't a hard deadline for the letter of rec yet, but I will update you if they tell us. I understand would not like to write me one, however. Thank you, professor. 

%Top student with 3.85
%- Studied abroad in Korea and was able to finish robotics concentration as 2/C
%- Got a broader perspective from his studies in Korea that will be valuable to share at NPS 
%- Taking Engineering Economics concentration to which has intrigued his curiosity to deepen his knowledge in the Operations Research Analysis (the master's degree I want to pursue)
%- Responsible for optimizing flight operations, battery life, drone stability for capstone project which shows his continued interest in Operations Research
%- Open to sharing knowledge to others both in the major and back in Bancroft
%- Served as Company Academics Officer, Company Admin Chief, Korean American Midshipmen Association Operations Officer, and currently serving as a squad leader in company. I am growing as a leader and student and able to balance both school and billet without compromising my intellectual curiosity. 
%- Displays organizational skills and consistent responsibility (based on you observation of running minutes and agenda for capstone meetings)

%I dont have a CV right now, but I will try making one asap. The application has general questions about why I want to pursue the masters degree program, but nothing in regards to a specific thesis supervisor. 